---
title: "WORKING TITLE: The adaptive value of green nest material across birds: A systematic review and meta-analysis"
authors:
  - name: Shreya Dimri
    affiliation: Department of Evolutionary Biology, Bielefeld University, Bielefeld, Germany
    corresponding: true
  - name: Tuba Rizvi
    affiliation: Department of Evolutionary Biology, Bielefeld University, Bielefeld, Germany
  - name: Júlio Segovia
    affiliation: Department of Evolutionary Biology, Bielefeld University, Bielefeld, Germany
  - name: Alfredo Sánchez-Tójar
    affiliation: Department of Evolutionary Biology, Bielefeld University, Bielefeld, Germany
    
bibliography: references.bib
---

```{r Setup, include=FALSE, echo=FALSE}

pacman::p_load(readr)

```

# Methods (\~2200 words)

Registration and Reporting

We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024]. We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @figsupp-checklist). All resources associated with this study, including data and code, are available at \[<https://github.com/shreyadimri/Green_Nest_Material>\] (insert Zenodo citation later).

## Systematic Review

### Literature search

```{r load search data, include=FALSE, echo=FALSE}

unique_reference_list <- read_csv("data/unique_reference_list.csv")

```

We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 and updated it on 12.08.2024. The search query was designed in three blocks to included terms for predictor/treatment ("green*" OR "herb*" OR "aromatic*" AND "nest*"), population of interest ("bird*" OR "aves" OR "avian" OR "ornithol*" OR "passerine*" OR "passeriform*" OR "songbird*" OR list of all bird genera) and only experimental studies ("experiment*" OR "manipulat\*") (for complete search string details see @figsupp-string). We searched the title, abstract and keywords in English language only. Our search found `{r} nrow(unique_reference_list)`

#### Literature search

We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022

Eligibility criteria

#### Study selection and eligibility criteria

-   Keyword search: where and when..

-   Justification for development of keyword search

-   Findings/Results of search

-   Exclusion criteria

-   How many papers in final meta-analysis and how many effect sizes

-   PRISMA Diagram link

### Data Extraction

-   What did we extract in priority order

-   Wrote to authors for missing info, used methods to deal with missing info

-   Figures extraction

-   Moderators extracted

### Effect size calculation

### Meta-analysis and meta-regressions

-   main effect model

-   meta-regressions for testing hypothesis

-   meta-regressions for exploratory analyses

Senstivity analysis and Publication Bias Test

### Deviations from registration

## Supplementary Appendix

<details>

<summary>Supplementary materials</summary>

{{< include supplementary_appendix.qmd >}}

</details>
